%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{ragged2e}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Vaigarai Sathi} \\ \vspace{1pt}
    \small 201-448-6477 $|$ \href{mailto:vaigarai.sathi@nyu.edu}{\underline{vaigarai.sathi@nyu.edu}} $|$ 
    \href{https://linkedin.com/in/vaigaraisathi}{\underline{linkedin.com/in/vaigaraisathi}} $|$
    \href{https://github.com/dawnorak}{\underline{github.com/dawnorak}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {New York University}{New York, NY}
      {Master of Science in Computer Science $|$ GPA: 3.95/4}{Sept. 2024 -- May 2026}
    \resumeSubheading
      {Woxsen University}{Hyderabad, India}
      {Bachelor of Science in Computer Science and Engineering $|$ GPA: 3.75/4}{Sept. 2020 -- May 2024}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Quantitative Research Intern}{New York, NY}
      {Blockhouse Labs, Inc.}{June 2025 -- Present}
      \resumeItemListStart
      \justifying{
        \resumeItem{Engineered advanced trading strategies and algorithms for a multi-venue Smart Order Router (SOR), optimizing execution across equities, crypto, and derivatives.}
        \resumeItem{Implemented an affine alpha integration process with a TWAP-based scheduler, utilizing a convex optimization approach for efficient slippage reduction and risk control.}
        \resumeItem{Designed a real-time policy engine that dynamically adjusts routing logic in \(<\) 10 ms based on market microstructure signals (order book imbalance, tick volatility), reducing adverse selection costs by 23\% during high-volatility periods.}
        \resumeItem{Accelerated SOR decision-making by 17\% by developing an ML-based lookup model to replace a traditional analytical solver, enabling faster and more accurate responses to market events.}
        }
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Machine Learning Intern}{Hyderabad, India}
      {Onward Assist}{Jan. 2024 -- July 2024}
      \resumeItemListStart
        \resumeItem{Engineered scalable container orchestration on AWS ECS for ML workloads, boosting efficiency for concurrent requests.}
        \resumeItem{Led migration from AWS to GCP, architecting robust and scalable workloads from scratch on Kubernetes Engine.}
        \resumeItem{Enhanced the pathology application by integrating DICOM compatibility for handling of medical imaging data.}
        \resumeItem{Developed a comprehensive format conversion pipeline on GCP using the Cloud Healthcare API.}
    \resumeItemListEnd

    \resumeSubheading
      {SDE Intern}{Hyderabad, India}
      {Effigo Global}{Jan. 2023 -- July 2023}
      \resumeItemListStart
        \resumeItem{Modernized legacy Spring Boot applications by upgrading the tech stack and developing RESTful APIs.}
        \resumeItem{Managed AWS instances and Docker container deployments to enhance application performance and scalability.}
        \resumeItem{Architected a reusable mailing service component, incorporating open-source editors and automated mailing features.}
        \resumeItem{Optimized Jenkins CI/CD pipelines with automated builds and notifications to improve cross-team collaboration.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/dawnorak/gt_covariance}{Spatio-Temporal Graph Learning for Covariance Forecasting}} $|$ \emph{PyTorch, Transformers}}{}
          \resumeItemListStart
            \resumeItem{Constructed dynamic graph-based representations of financial markets using S\&P 500 assets as nodes with multi-source features (price/volume derivatives, fundamentals), and edges derived from rolling correlations.}
            \resumeItem{Developed a Spatio-Temporal Graph Transformer combining GATv2 and Transformer encoders to model both inter-asset dependencies and temporal dynamics for high-resolution covariance matrix forecasting.}
            \resumeItem{Enforced positive semi-definiteness in covariance outputs via low-rank factorization and spectral regularization, optimizing log-likelihood-based loss with Ledoit-Wolf-style shrinkage to achieve robust, interpretable risk modeling.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://github.com/dawnorak/marl-kart-simulator}{Cooperation Dynamics in Multi-Agent Systems}} $|$ \emph{Unity, C\#, PyTorch}}{}
          \resumeItemListStart
          \justifying{
            \resumeItem{Research paper presented at the MAD-Games Workshop at IROS 2023, and journal article published in SAE International Journal of Connected and Automated Vehicles.}
            \resumeItem{Explores strategies to promote cooperation in multi-agent systems, focusing on game-theoretic scenarios.}
            \resumeItem{Leveraged mean-field game theory for establishing equilibrium solutions and reward structures in infinitely large agent sets in repeated games, along with the validation of their practical capabilities using various simulations.}
            }
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.0in, label={}]
    \small{\item{
     \textbf{Languages}{: C, C++, HTML/CSS, Java, JavaScript, Python} \\
     \textbf{Technologies/Frameworks}{: Flask, Node.js, PyTorch, React, Spring Boot, SQL, Tensorflow, Unity} \\
     \textbf{Development Tools}{: Amazon Web Services, Docker, Figma, Git, Google Cloud Platform, Jenkins, Kubernetes}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}